%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:
%%%%%%%%
%%%%%%%%\bibliographystyle{model1-num-names}
%%%%%%%%\bibliography{sample.bib}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1-num-names.bst.

%% References without bibTeX database:

\begin{thebibliography}{00}

%\bibitem{SORA}S.A. Garcia Morelos, F.Brooks, S.Oliver, A.Walker, K.D. Portillo, R.B. Masek, D.Mroczek, D.Pena, J.Juarez, A.Cruz, D. Henandez, S.George, D. Pattison, A.L.Renshaw. \textit{Scientific Report for the UH Team.} SORA 2017 Mission Webpage. \textit{http://laspace.lsu.edu/hasp/groups/Payload.php?py=2017&pn=10}.

\bibitem{minipix}MiniPIX - Miniaturized Portable USB Photon Counting Camera. (n.d.). Retrieved February 02, 2017, from \textit{http://advacam.com/camera/minipix}.

\bibitem{timepixiss} Stoffle, N., Pinsky, L. et al. Timepix-based radiation environment monitor measurements aboard the International Space Station. Nucl. Instrum. Methods Phys.
Res., A, 782 (2015):143.

\bibitem{aircrewexposure} B.J. Lewis, M.J. McCall, A.R. Green, L.G.I. Bennett, M. Pierre, U.J. Schrewe, K. O'Brien, E. Felsberger; Aircrew Exposure from Cosmic Radiation on Commercial Airline Routes, Radiation Protection Dosimetry, Volume 93, Issue 4, 1 February 2001, Pages 293–314, \url{https://doi-org.ezproxy.lib.uh.edu/10.1093/oxfordjournals.rpd.a006442}
\bibitem{timepixdosimetry} Carlos Granja, Stanislav Pospisil,
Quantum dosimetry and online visualization of X-ray and charged particle radiation in commercial aircraft at operational flight altitudes with the pixel detector Timepix,
Advances in Space Research,
Volume 54, Issue 2,
2014,
Pages 241-251,
ISSN 0273-1177,
https://doi.org/10.1016/j.asr.2014.04.006.
(http://www.sciencedirect.com/science/article/pii/S0273117714002208)
Keywords: Radiation detection; Radiation exposure at aviation altitudes; Dose equivalent rate; Semiconductor pixel detector; Quantum dosimetry

\bibitem{advacam}
  ADVACAM at \url{http://www.advacam.com}

\bibitem{medipix}
  Medipix collaboration at \url{https://medipix.web.cern.ch/}.
  
\bibitem{stuartthesis} 22
  George, S., \textit{Dosimetric Applications of Hybrid Pixel Detectors}, University of Wollongong, Australia, 2015.

\bibitem{mpdatasheet}
  ADVACAM, \textit{MINIPIX Version 1.0 Datasheet}, Retrieved from \url{http://www.widepix.cz/files/datasheets/MiniPIX\%20v1.0\%20Datasheet.pdf}.

\bibitem{mpjakubek}
  Jan Jakubek, \textit{Precise energy calibration of pixel detector working in time-over-threshold mode} Institute of Experimental and Applied Physics, Czech Technical University in Prague, Czech Republic, 2011.

\bibitem{bexus}
Urbar, J., Scheirich, J., Jakubek, J., 2011. Medipix/Timepix cosmic ray tracking on BEXUS stratospheric balloonflights. Nucl. Instrum. Methods A 633, S206-209.
  
\bibitem{hasp}
http://laspace.lsu.edu/hasp/
\end{thebibliography}
